Follow-up Samples

### 2016-12-15 submission/manuscript_outline_20161024.Rmd

---
title: ''
csl: mbio.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
geometry: margin=1.0in
bibliography: null
---

>>>>

---
title: ''
csl: mbio.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
geometry: margin=1.0in
bibliography: reference.bib
---
